Log

### 2022-09-16 Resources/LogJournal.Rmd
Added the column names to the dataset
Made my own codebook and loaded in the data

1.  Sequence Name: Accession number for the SWISS-PROT database  
2.  mcg: McGeoch's method for signal sequence recognition.  
3.  gvh: von Heijne's method for signal sequence recognition.  
4.  alm: Score of the ALOM membrane spanning region prediction program.  
5.  mit: Score of discriminant analysis of the amino acid content of the N-terminal region (20 residues long) of mitochondrial and non-mitochondrial proteins.  
6.  erl: Presence of "HDEL" substring (thought to act as a signal for retention in the endoplasmic reticulum lumen). Binary attribute.  
7.  pox: Peroxisomal targeting signal in the C-terminus.  
8.  vac: Score of discriminant analysis of the amino acid content of vacuolar and extracellular proteins.  
9.  nuc: Score of discriminant analysis of nuclear localization signals of nuclear and non-nuclear proteins.  
10. Class Distribution: The class is the localization site. Consisting of:

@@

```{r}
data <- as_tibble(read.table("yeast.data", sep = ""))
```

>>>>

1.  Sequence Name: Accession number for the SWISS-PROT database.  
2.  mcg: McGeoch's method for signal sequence recognition.  
3.  gvh: von Heijne's method for signal sequence recognition.  
4.  alm: Score of the ALOM membrane spanning region prediction program.  
5.  mit: Score of discriminant analysis of the amino acid content of the N-terminal region (20 residues long) of mitochondrial and non-mitochondrial proteins.  
6.  erl: Presence of "HDEL" substring (thought to act as a signal for retention in the endoplasmic reticulum lumen). Binary attribute.  
7.  pox: Peroxisomal targeting signal in the C-terminus.  
8.  vac: Score of discriminant analysis of the amino acid content of vacuolar and extracellular proteins.  
9.  nuc: Score of discriminant analysis of nuclear localization signals of nuclear and non-nuclear proteins.  
10. Class Distribution: The class is the localization site. Consisting of (abbreviation (full name) the amount):

@@

## EDA of the yeast data

Since there is not a codebook. I created my own codebook.

```{r}
attr_names <- c("seq.name", "mcg", "gvh", "alm", "mit", "erl", "pox", "vac","nuc", "loc.site" )
data_types <- c("str", "int", "int", "int", "int", "int", "bool", "int", "int", "factor")
data_labels <- c("Accession number for the SWISS-PROT database",
                                    "McGeoch's method for signal sequence recognition", 
                                    "von Heijne's method for signal sequence recognition", 
                                    "Score of the ALOM membrane spanning region prediction program",
                                    "Score of discriminant analysis of the amino acid content of the N-terminal region",
                                    "Presence of 'HDEL' substring",
                                    "Peroxisomal targeting signal in the C-terminus",
                                    "Score of discriminant analysis of the amino acid content of vacuolar and extracellular proteins",
                                    "Score of discriminant analysis of nuclear localization signals of nuclear and non-nuclear proteins",
                                    "The class is the localization site")
codebook <- data.frame(Name=attr_names, Fullname=data_labels, Datatypes=data_types)

knitr::kable(codebook)
```

Here is the codebook. With the attributes abbreviation, explanation and data types. As you can see there are many int types.

Now we need to load in the data. And change the column names to the attributes abbreviation, since these are non-existent.

```{r}
data <- as_tibble(read.table("yeast.data", sep = ""))
colnames(data) <- attr_names

str(data)
```

As you can see, the last column, loc.site, consists of characters, but this one needs to be converted to factors for clarity and complexity.

```{r}
data$loc.site <- as.factor(data$loc.site)
str(data$loc.site)
```

As you can see the data type of the column loc.site has been succesfully changed to factors.
